\subsection{Regulatory policies}
The CLup application will ask for user personal information like name, surname, email address, and phone number. Phone numbers and email addresses won't be used for commercial purposes.
Personal information will be processed in compliance with the GDPR.

Moreover, the system will have to ask for users' permission to retrieve and use their position. GPS positions will be stored for as long it's needed to compute the route to the grocery store.

\subsection{Hardware limitations}
\label{hardware limitations}
\begin{itemize}
    \item Mobile application
    \begin{itemize}
        \item iOS or Android smartphone
        \item 2G/3G/4G/Wi-Fi Internet connection
        \item GPS
    \end{itemize}
    \item Web application
    \begin{itemize}
        \item Modern web browser
    \end{itemize}
\end{itemize}

\subsection{Interfaces to other applications}
In the first release of CLup no public interfaces will be opened to third party services.

\subsection{Text assumptions}
In the specification document presented by the client, we found some points that lacked precision. To better clarify and to make you understand better the content of this document we decided to introduce those assumptions.
\begin{itemize}
    \item Entrances monitoring is referred to customers using their QR code.
    \item QR Code scanning is not mandatory: customers who will scan their QR code when entering the store will contribute to entrances monitoring, those who will not contribute to such statistics.
    \item Visits durations for long term customers are computed by the CLup system from previous visits details inserted by the users
\end{itemize}

\subsection{Domain assumptions}

    \begin{center}
        {\renewcommand{\arraystretch}{2}%
        \begin{longtable}{L{2cm}L{12cm}}
            \hline
            \textbf{D1} & All customers use CLup to access the store \\
            \hline
            \textbf{D2} & The CLup line up system is enabled only when entrances control is needed \\
            \hline
            \textbf{D3} & Store has a capacity greater than 0 \\
            \hline
            \textbf{D4} & GPS is enabled between the line up request and the departure to approach the store \\
            \hline
            \textbf{D5} & The user has a working internet connection \\
            \hline
            \textbf{D6} & The store has an available employee to serve customers who physically want to line up and retrieve a number \\
            \hline
            \textbf{D7} & The store has an available employee to check for entrances and to report exits \\
            \hline
            \textbf{D8} & The store employee who lines up customers will call them when they are allowed to enter the store \\
            \hline
            \textbf{D9} & Stores are uniquely identified \\
            \hline
            \textbf{D10} & The customer's device, the store and the CLup system have a syncronized date and time \\
            \hline
            \textbf{D11} & A QR code scanner will be available entering the store \\
            \hline
            \textbf{D12} & The store is physically accessible \\
            \hline
            \textbf{D13} & There is a route from the customer to the store \\
            \hline
            \textbf{D14} & The estimated time to enter the store is greater than the estimated time to approach the store \\
            \hline
            \textbf{D15} & The customer stay at the store is limited in time \\
            \hline
            \textbf{D16} & No two customers have the same number when entering at the same time \\
            \hline
            \textbf{D17} & The customer who specifies what he/she will buy/what departments he/she will go to will comply with his/her estimations \\
            \hline
            \textbf{D18} & Customer who wants to directly interact with the CLup system has a compatible device \\
            \hline
            \textbf{D19} & Store has a CLup compatible device \\
            \hline
        \end{longtable}}
    \end{center}