Here is the description of the major functions that the CLup system has. In particular, we identified four significative functions, they are:
\begin{itemize}
    \item \textbf{Line up:} This is the main function of the CLup system. The application works as a digital counterpart to the common situation where people who are in line for a service retrieve a number that gives their position in the queue. \newline To do that, the application allows customers to line up, retrieving a number, for a store that has joined to CLup and it provides to alert the customer when his turn is coming.
    \item \textbf{Book a visit:} Another main functionality the application has, is to book a visit. Similar to booking a slot for visiting a museum, customers can choose a time slot in which to visit the supermarket. The system can schedule customer visits correctly given that each visit will last differently from the others. CLup asks the customer details about his/her visit or it computes an estimated duration from previous visits of the same user
    \item \textbf{Identification of customers at the store entrance:} The system allows customers to generate a QR code for their entrance into the supermarket, it is optional and customers are not obliged to do so. This QR code allows the store to identify the customer is entering the supermarket. For those who do not generate the QR code to enter after a queue, it will not be possible to identify them because their access will be exclusively through the generated number
\end{itemize}