This document is composed by six chapters :
\begin{itemize}
    \item \textbf{Chapter 1: Introduction.} This chapter includes the goals of the project (\textit{Purpose}) 
    and an analysis of the world and of the shared phenomena (\textit{Scope}). It also includes a section where 
    there are all the descriptions, acronyms, and abbreviations in the document. Lastly, there 
    is a revision history and a reference documents list
    \item \textbf{Chapter 2: Overall Description.} This chapter includes scenarios and further
    details on the shared phenomena and a domain model (class diagrams and statecharts) (\textit{Product perspective}). It also
    shows the most important requirements (\textit{Product functions}). It clarifies the user needs (\textit{User charateristics}), and lastly, it contains 
    the domain assumptions (\textit{Assumptions, dependencies and constraints})
    \item \textbf{Chapter 3: Specific Description.} This chapter is the body of the documents. It includes a section for 
    the User, Hardware, Software and Communication Interfaces (\textit{External Interface Requirements}). It also contains a definition
    of use case diagrams, use cases, and associated sequence/activity diagrams, and a map on requirements (\textit{Functional Requirements}).
    Lastly, there are three sections dedicated to non-functional requirements (\textit{Performance Requirements}, \textit{Design Constraints} \textit{Software System Attributes})
    \item \textbf{Chapter 4: Formal Analysis Using Alloy.} This chapter includes a brief presentation of the
    main objectives driving the formal modeling activity, as well as a description of the model.
    itself, what can be proved with it, and why what is proved is important given the problem at hand. It also includes some worlds obtained by running the
    formal model and the results of the checks performed on meaningful assertion
    \item \textbf{Chapter 5: Effort Spent.}  This chapter includes information about the number of hours each group member has worked for this document
    \item \textbf{Chapter 6: References.}
\end{itemize}