This document is composed of six chapters :
\begin{itemize}
    \item \textbf{Chapter 1: Introduction.} This chapter describes the scope and the purpose of this DD. This chapter also includes the structure of the document and a set of definitions, acronyms and abbreviation used
    \item \textbf{Chapter 2: Architectural Design.} This chapter contains the architectural design choice, it includes an overview of the designed architecture, all the components, the interfaces, and the technologies used for the design of the application. It also includes the main functions of the interfaces and the process in which they are utilized (Runtime view and component interfaces). Finally, there is an explanation of the design pattern chosen and recommended to develop the system
    \item \textbf{Chapter 3: User Interface Design.} This chapter shows how the UI has to look like. It completes and deepens to the User Interfaces (3.1.1) subsection in the RASD
    \item \textbf{Chapter 4: Requirements Traceability.} This chapter explains how the requirements defined in the RASD map to the design elements defined in this document
    \item \textbf{Chapter 5: Implementation, Integration and Test Plan.} Here is the order in which is planned to implement the subcomponents of the system and the order in which is planned to integrate such subcomponents and test the integration
    \item \textbf{Chapter 6: Effort Spent.}  This chapter includes information about the number of hours each group member has worked for this document
    \item \textbf{Chapter 7: References.}
\end{itemize}